### 2022-11-15 NSF2022/Description/backgroundv3.tex
touch up
...

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is highly desirable
from the Applied Mathematics point of view as there are many
\emph{Further Applications}, such as (i) amphiphilic Janus spheres that
form diverse suprastructures~\cite{HaBr20, McBr21, Bradley2017}, (ii)
pickering emulsions involving two-phase fluids and dense suspensions
\cite{Bradley2016}, (iii) creation and manipulation of small droplets
using amphiphilic microparticles~\cite{Ha2022SurfaceEM,
Ha2020MinimalSC}, and (iv) tension driven fabrication of
microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,
Zeng20223DprintedMT, Russell2016EnergyLF}.

@@

\subsection{Outline of the proposal}
The aim of this proposal is to advance the theory, simulation and
modeling for soft-matter systems and foster training in Mathematical
Sciences.
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, and
scientific computing. The PIs' recent collaborative
works~\cite{FuQuRyYo22, fu-ryh-qua-you2022,FuQuRyYo22}
are a solid foundation for the proposed research.

Section~\ref{sec:BroaderImpacts} summarizes the broader
impacts and section~\ref{sec:IntellectualMerit} summarizes the
intellectual merit of our research activity.
Section~\ref{sec:proposed-work} contains our specific aims.

>>>>

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is highly desirable
from the Applied Mathematics point of view as there are many
\emph{Further Applications}, such as (i) amphiphilic Janus spheres that
form diverse suprastructures~\cite{HaBr20, McBr21, Bradley2017}, (ii)
pickering emulsions involving two-phase fluids and dense suspensions
\cite{Bradley2016}, (iii) creation and manipulation of small droplets
using amphiphilic microparticles~\cite{Ha2022SurfaceEM,
Ha2020MinimalSC}, and (iv) tension driven microfabrication
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,
Zeng20223DprintedMT, Russell2016EnergyLF}.

@@

\subsection{Outline of the proposal}
The aim of this proposal is to advance the theory, simulation and
modeling for soft-matter systems and foster training in Mathematical
Sciences.
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, and
scientific computing. The PIs' recent collaborative
works~\cite{FuQuRyYo22, fu-ryh-qua-you2022}
are a solid foundation for the proposed research.
Section~\ref{sec:BroaderImpacts} summarizes the broader
impacts and section~\ref{sec:IntellectualMerit} summarizes the
intellectual merit of our research activity.
Section~\ref{sec:proposed-work} contains our specific aims.
